---
title: "Development actions history"
output: html_document
editor_options: 
  chunk_output_type: console
---

All commands that you use to use when developing packages...

# First time just after creating the project

- Fill the following chunk to create the DESCRIPTION of your package

```{r description}
# Describe your package
fusen::fill_description(
  pkg = here::here(),
  fields = list(
    Title = "Templates and Workflows for Data Science Projects",
    Description = "Use templates to make common data science workflows easier.",
    `Authors@R` = c(
      person("Fabian", "Distler",
        email = "fabian.distler@gmx.net",
        role = c("aut", "cre", "cph"), comment = c(ORCID = "0000-0002-1438-0724")
      )
    )
  )
)
# Define License with use_*_license()
usethis::use_mit_license("Fabian Distler")
```

# Start using git

```{r, eval=FALSE}
usethis::use_git()
# Deal with classical files to ignore
usethis::git_vaccinate()
# Use main for primary branch
usethis::git_default_branch_rename()
```

# Set extra sources of documentation

```{r, eval=FALSE}
# Install a first time
remotes::install_local()
# README
usethis::use_readme_rmd()
# Code of Conduct
usethis::use_code_of_conduct("fabian.distler@gmx.net")
# NEWS
usethis::use_news_md()
# Package structure (add this in a dev/Readme.md file)
fusen::draw_package_structure()
```

**From now, you will need to "inflate" your package at least once to be able to use the following commands. Let's go to your flat template, and come back here later if/when needed.**


# Package development tools
## Use once

```{r, eval=FALSE}
# package-level documentation
usethis::use_package_doc()

# GitHub
# Add your credentials for GitHub
usethis::create_github_token()
gitcreds::gitcreds_set()

# _Or one step at a time
# Send your project to a new GitHub project (included in `init_share_on_github()`)
usethis::use_github()

# Set Continuous Integration
usethis::use_github_action("pkgdown")
usethis::use_github_action("test-coverage")
usethis::use_github_action("pr-commands")
usethis::use_github_action("style")

# Chores.
usethis::use_tidy_contributing()
usethis::use_tidy_issue_template()
usethis::use_tidy_github_labels()
usethis::use_lifecycle()
```

## Use everytime needed

```{r, eval=FALSE}
# Chores.
usethis::use_tidy_upkeep_issue()
usethis::use_lifecycle_badge("experimental")
usethis::use_tidy_description()

# Generate documentation and deal with dependencies
attachment::att_amend_desc()

# Add a new flat template
fusen::add_flat_template("add")
```

# Share the package

```{r, eval=FALSE}
# set and try pkgdown documentation website locally
usethis::use_pkgdown()
pkgdown::build_site()

# build the tar.gz with vignettes to share with others
devtools::build(vignettes = TRUE)

# Share your package and its documentation on GitHub
# usethis::create_github_token()
# gitcreds::gitcreds_set()
fusen::init_share_on_github()
```
