---
title: Model Workflow For Inference
author: "John Doe"
date-modified: "`r paste('Last rendered:', Sys.Date())`"
keep-md: false
format: 
  html:
    default: true
    code-fold: true
    toc: true
    self-contained: true
    fig-width: 6
    fig-asp: 0.618
    out-width: "70%"
    fig-align: center
    highlight-style: github
  pptx:
    # reference-doc: template.pptx can add template to folder or quarto
    fig-format: png
    fig-dpi: 300
    fig-width: 10
    fig-asp: 0.618
    fig-align: center
---

```{r setup, include=FALSE}
# Ensures the package "pacman" is installed
if (!require("pacman")) install.packages("pacman")

# Add needed packages here
pacman::p_load()
```

# Load cleaned data.
```{r}
df <- rio::import(df_cleaned)
```

# Prepare data.
```{r}
# Select outcome and potential predictors.
df_model <- df |>
  select() |>
  # If no imputation is used we need to do a complete case analysis. There are
  # no missing values allowed anywhere.
  drop_na()
```

At this point, we are looking for very obvious problems, such as values
that are highly unusual, extremely skewed variables, or categorical variables
with sparse levels. We also want to check that all categorical variables are
coded as factors.


# Univariate analysis
```{r}
# Only use predictors with p < 0.25
gtsummary::tbl_uvregression(
  method = glm, ## define regression want to run (e.g. generalised linear model)
  y = outcome,
  method.args = list(family = binomial), ## define what type of glm want to run
  exponentiate = TRUE ## exponentiate to produce odds ratios (rather than log odds)
) |>
  gtsummary::bold_p(t = 0.25)
```

# Fit model
Refer to https://www.bookdown.org/rwnahhas/RMPH/overview-taxonomy.html for
help on deciding which model to choose
```{r}
m1 <- lm(y ~ ., data = df_model)
```


## Check model assumptions
How to fix problems: https://easystats.github.io/performance/articles/check_model.html
```{r}
performance::check_model(m1)

# Only keep significant predictors unless good reason to keep them.
performance::check_model(m1) # again and see if improved
```

## Show model results.
```{r}
parameters::model_parameters(m1)
easystats::model_dashboard(m1)
gtsummary::tbl_regression()
```

# Compare different models.
```{r}
performance::compare_performance(m1, m2, m3, m4, rank = TRUE)
parameters::test_performance()
```

# Automatic reports
# Can use report package for automatic report.
```{r}
report::report(m1)
```

## Tricks
Add conditional wrappers to only render chunks for certain formats. E.g. you
only want to render certain chunks for Powerpoint and all chunks for html:
<!-- ::: {.content-visible when-format="html"} -->
<!-- ::: -->
Then add slides like this

## Slide title
slide content
